### 2023-12-19 manuscript.tex
Autocommit

In this study, we focused on women’s intention of whether they will have their daughter’s genital modified in the context of group FGC norms and geographic estimates of community FGC prevalence.  The research presumption was based on the studies aforementioned that women’s intention on practicing FGC on their daughters was dependent on other women’s intention of this practice \cfonly{descriptive norms?!} in their community. We used index of attitudinal evaluation of FGC benefits to represent FGC norm.  Attitudes is a sensible proxy of social norm \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} and has been applied on fgc studies \cite{CislHeis18, EffeVogt15, Harf06, ModrLiu13, PashPonn16, ShelHern06,}} \cfonly{check cites}.  However, there has bee little quantitative research on the relationship between attitudes and intention of cutting daughters at both an individual and community level incorporating beliefs of FGC benefits.

There were three models in this study:  the daughter model, the continuance model and the persistence model.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and behavioral intention to have their daughters receiving FGC.  Additionally, we decomposed the model into two “structural” models:  structural one “continuance” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “persistence”  model \cf{or “mixed” model?} to examine the association of beliefs of FGC benefits, FGC continuance and intention of genitally cutting daughters.  We used the two structural models to further understand how such positions change the main model.

@@

We analyzed the secondary data of women aged 15-49 in the Demographic and Health Surveys (DHS).  The DHS was selected when it met the study criteria:  countries with high FGC prevalence \cite{UNIC16} with the modules of FGC benefit and gender awareness. Four countries qualified under this criteria with the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  \cfcmt{checked and updated in Nov 6, 2023.   The datasets are pretty old but were the most recent ones with FGC benefits modules.  See FGC main page for updated info.}.  Since one of our main research interests was to detect relationship of normative attitudes and intentional behaviors of circumcising daughters, the findings should not be compromised due to the time of the data collected.

Only women with daughters to be considered for FGC were included in the the daughter model and the persistence model.   The continuence model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7231 in Kenya, Mali, Nigeria and Sierra Leon respectively.  \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

@@

Our main response variables were woman's reported intention to modify their daughters’ genitals in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the future in the persistence model.  Co-variables in the models were sample’s fgc status, beliefs of fgc benefit, country, gender awareness, education, media, job, residence (rural vs. urban), religion, marital status, age, wealth; in order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?} with cluster as a proxy to represent a community level of impact \cite{AligRen06, BoylSvec19, Hayf05, Krav02}.  In addition, daughter fgc plan at a group level was added to daughter model; persistence at a group level to persistence model; and daughter fgc plan at a group level, persistence and persistence at a group level to mixed model.

Woman's FGC status and beliefs of FGC benefits (see supp for the benefit questionnaire) were our the main predictors.  The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of fgc beliefs associating with FGC practice.  We included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s gender awareness would moderate \cf{wording?} their intention of cutting their daughters’ genitals and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} check and cut}.  Media use and gender awareness were both scored.  Cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it) were treated as random variables.  We treated ethnicity as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity \cite{Hayf05}.

>>>>

The research presumption was based on the studies aforementioned that women’s intention on practicing FGC on their daughters was dependent on other women’s intention of this practice \cfonly{descriptive norms?!}. We used index of attitudinal evaluation of FGC benefits to represent FGC norm.  Attitudes is a sensible proxy of social norm \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} and has been applied on fgc studies \cite{CislHeis18, EffeVogt15, Harf06, ModrLiu13, PashPonn16, ShelHern06,}} \cfonly{check cites}.  However, there were little quantitative research on the relationship between attitudes and intention of circumcising daughters at both an individual and community level while taking beliefs of FGC benefits into account.

Three models were constructed in response to the three research questions mentioned above:  the daughter model, the continuance model and the persistence model.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and behavioral intention to have their daughters receiving FGC.  Additionally, we decomposed the model into two “structural” models:  structural one “continuance” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “persistence”  model \cf{or “mixed” model?} to examine the association of beliefs of FGC benefits, FGC continuance and intention of genitally cutting daughters.  We used the two structural models to further understand how such positions change the main model.

@@

We analyzed the secondary data of women aged 15-49 from the Demographic and Health Surveys (DHS).  The data was selected when it met the research criteria:  countries with high FGC prevalence \cite{UNIC16}, and with the modules of FGC status and benefit and gender awareness. Four countries qualified under this criteria with the most recent data sets: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008 \cfcmt{checked and updated in Nov 6, 2023.}   Although the datasets seemed outdated, but it should not affect the study object which was about FGC norms and behaviors.  \cfcmt{See https://github.com/fishforwish/fgc/blob/master/README.md for updated info}.

Only women with daughters for for FGC options were included in the the daughter model and the persistence model.   The continuance model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7231 in Kenya, Mali, Nigeria and Sierra Leon respectively.  \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

@@

The main response variables were woman's reported intention to modify their daughters’ genitals in the daughter model and the persistence model, and woman's attitude on FGC future in the continuance model.  The main predictors were woman's FGC status and beliefs of FGC benefits (see supp for the benefit questionnaire).  The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of fgc beliefs associating with FGC practice.

Co-variables in the models were basic social demographic variables (country, gender awareness, education, media, job, residence (rural vs. urban), religion, marital status, age, and wealth).  We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s gender awareness would associate with their intention of cutting daughters’ genitals and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} check and cut}.  Cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it) were treated as random variables.  We treated ethnicity as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity \cite{Hayf05}.

Regarding potential community impact on the practice of FGC, the models also teated education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level \cfcmt{on a cluster level, not national, right?} with cluster as a proxy to represent a community level of impact \cite{AligRen06, BoylSvec19, Hayf05, Krav02}.

In addition, daughter fgc plan at a group level was added to daughter model; persistence at a group level to persistence model; and daughter fgc plan at a group level, persistence and persistence at a group level to mixed model.  Media use and gender awareness were also scored.
